

Using PSID in 2013, we estimate the married women's wage in the presence of
high-dimensional controls and possible sample selection bias.  

The selection equation is about whether women choose to work. It has many 
potential controls, including the continuous variables and dummy variables.
The main Equation is about married women's wages. The variables of interests
are experience ({\tt expr}), experience squared ({\tt $exper^2$}), education
level in years ({\tt educ}), age ({\tt age}), age squared ({\tt $age^2$}), and
whether work for the government ({\tt govern}).

We estimate four models. 
\begin{itemize}
\item Model 1 has many controls in the selection-equation.  

\item Model 2 is basically the same as Model 1, but it includes some extra
controls in the main Equation. These controls are current living state ({\tt
state}), race ({\tt race}), and occupation categories ({\tt occ}). 

\item Model 3 is basically the same as Model 1, but we add race ({\tt race}) as
variable of interest in the main Equation.

\item Model 4 is basically the same as Model 3, but we add extra controls in the
main Equation. These controls are current living state and occupation
categories.
\end{itemize}


\subsection{Estimation results}
First, we define the potential controls in the selection equation.
\begin{stlog}
\input{tables/log1.log.tex}
\end{stlog}

We estimate Model 1 using a double-selection-lasso Heckman. There are 92
controls and Lasso selects 24 of them.  The estimate for $\lambda$ is
significant at $5\%$ level.  It indicates sample selection bias.

\begin{stlog}
\input{tables/log2.log.tex}
\end{stlog}

In Model 2, we now include extra controls such as current living state, race,
and occupation in the main Equation. There are 173 controls in this model, and
Lasso selects 34 of them. Interestingly, the coefficient for {\tt govern}
becomes significant at \%10 levels in this model. The other coefficients do not
change much compared with Model 1.
\begin{stlog}
\input{tables/log3.log.tex}
\end{stlog}

In Model 3, we add race as a variable of interest in the main Equation, and
everything else is the same as Model 1.
\begin{stlog}
\input{tables/log4.log.tex}
\end{stlog}

In Model 4, we add extra controls, such as the living state and occupation
category, in the main Equation. Everything else is the same as Model 3.
\begin{stlog}
\input{tables/log5.log.tex}
\end{stlog}


Here are the estimation results of all models.
\begin{stlog}
\input{tables/log6.log.tex}
\end{stlog}

Finally, if we try to estimate Model 1 using traditional Heckman, the probit for
the selection Equation does not even converge because of high-dimensional
controls. 
